---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# BMisc

BMisc includes miscellaneous functions for working with panel data, quantiles, and printing results.

## Installation

You can install BMisc from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bcallaway11/BMisc")
```

or from CRAN with:
```{r eval=FALSE}
install.packages("BMisc")
```

## Example 1

One of the most useful functions in the `BMisc` package is `makeDist` which takes a vector of observations and turns them into a distribution function.

```{r example1}
y <- rnorm(100)
y <- y[order(y)]
u <- runif(100)
u <- u[order(u)]
F <- makeDist(y,u)
class(F)
##plot(F)
```

## Example 2
Another useful function is the `makeBalancedPanel` function which drops observations from a panel dataset which are not available in all time periods.

```{r example2}
id <- rep(seq(1,100,1),2) ## individual ids for setting up a two period panel
t <- rep(seq(1,2),100) ## time periods
y <- rnorm(200) ## outcomes
dta <- data.frame(id=id, t=t, y=y) ## make into data frame
dta <- dta[-7,] ## drop the 7th row from the dataset (which creates an unbalanced panel)
nrow(dta)
dta <- makeBalancedPanel(dta, idname="id", tname="t")
nrow(dta) ## now all the observations with missing data in any period are dropped
```
